Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2018-12-19 paper/snakemajoranas.tex
Minor changes to manuscript

\date{\today}

\begin{abstract}
We are solving a problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
We do this by introducing a zigzag geometry.
This works because the maximum trajectory length is cut-off due to the geometry and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
In addition to having a large minimum energy gap, the absence of long length trajectories means that the localization length is very short as well.
\end{abstract}

@@

\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}

@@

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}

\comment{We consider a two-dimensional system with zigzag.}
We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
Similar to the straight system \cite{pientka2017topological}, a magnetic field $B_x$ pointed along the $x$ direction is applied.
We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term with a superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.

@@

\comment{We calculate the bandstructure for varying amount of zigzag.}
In figure \ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
As the zigzag introduces super cell, we see a folded bandstructure.
For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.

@@

\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
Similar to what is described in Pientka et. al [\cite{pientka2017topological}], we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.

@@

\comment{We use a short junction approximation and neglect transverse SO.}
We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}. 
For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
The result is specified in Eqs. \ref{eq:smatrix} to \ref{eq:momenta_short_junction}.

@@

\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
In figure \ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
All of the zigzag type geometries however show greatly reduced coherence length.
This can be explained by two effects: the increase in topological gap, but also the before mentioned reduction of the group velocity.

>>>>

\date{\today}
\begin{abstract}
We are solving a problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
We do this by introducing a zigzag geometry.
This works because the maximum trajectory length is cut-off due to the geometry and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
In addition to having a large minimum energy gap, the absence of long length trajectories means that the localization length is very short as well.
\end{abstract}

@@

@@

\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
Currently proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}
\comment{We consider a two-dimensional system with zigzag.}
We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
Similar to the straight system \cite{pientka2017topological}, a magnetic field $B_x$ pointed along the $x$ direction is applied.
We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term with a superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.

@@

\comment{We calculate the bandstructure for varying amount of zigzag.}
In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
As the zigzag introduces super cell, we see a folded bandstructure.
For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.

@@

\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
Similar to what is described in Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.

@@

\comment{We use a short junction approximation and neglect transverse SO.}
We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}. 
For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.

@@

\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
All of the zigzag type geometries however show greatly reduced coherence length.
This can be explained by two effects: the increase in topological gap, but also the before mentioned reduction of the group velocity.
